First Class Pattern Matching in a Deeply Embedded Domain Specific Language\\ \large{Not For Distribution}

### 2020-07-20 paper/paper.tex
More on the relationship with Church encodings

>>>>

Both of those representations represent the type as a function that performs the
corresponding case analysis. A deep embedding for the operations
\ttt{church\_mkLeft} and \\ \ttt{church\_mkRight} would look
like:

\begin{lstlisting}
data ChurchCoproduct r where
  Church_MkLeft
    :: a -> (a -> r) -> (b -> r) ->
       ChurchCoproduct r
  Church_MkRight
    :: b -> (a -> r) -> (b -> r) ->
       ChurchCoproduct r

church_coproductEval
  :: ChurchCoproduct r -> r
church_coproductEval (Church_MkLeft x f g)
  = f x
church_coproductEval (Church_MkRight y f g)
  = g y
\end{lstlisting}

If we factor out the data contained in these coproducts so that it is separated from the
case analysis functions, we can obtain

\begin{lstlisting}
data ChurchCoproductMatch t r where
  ChurchCoproductMatch
    :: (a -> r) -> (b -> r) ->
       ChurchCoproductMatch (Either a b) r

church_coproductMatchEval
  :: Either a b ->
     ChurchCoproductMatch (Either a b) r ->
     r
church_coproductMatchEval
    (Left x)
    (ChurchCoproductMatch f g)
  = f x
church_coproductMatchEval
    (Right y)
    (ChurchCoproductMatch f g)
  = g y
\end{lstlisting}
